TODO title

### 2017-01-12 doc/paper/paper.tex
Start writing paper.

\title{How to Make a Proceedings Paper Submission}

\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\
  Department of Psychology, 1202 W. Johnson Street \\
  Madison, WI 53706 USA
  \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\
  Department of Educational Psychology, 1025 W. Johnson Street \\
  Madison, WI 53706 USA}

@@

\section{General Formatting Instructions}

The entire contribution of a proceedings paper (including figures,
references, and anything else) can be no longer than six pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
  U.S. letter or A4 paper, so you must be sure to measure the width of
  the printed text.} Use 10~point Times Roman with 12~point vertical
spacing, unless otherwise specified.

The title should be in 14~point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11~point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10~point type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

\section{First Level Headings}

First level headings should be in 12~point, initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

\subsection{Second Level Headings}

Second level headings should be 11~point, initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~line
space below the heading.

\subsubsection{Third Level Headings}

Third level headings should be 10~point, initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

\section{Formalities, Footnotes, and Floats}

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
\citeA{NewellSimon1972a}, but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
\cite{NewellSimon1972a}. List multiple references alphabetically and
separate them by semicolons
\cite{ChalnickBillman1988a,NewellSimon1972a}. Use the
``et~al.'' construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9~point type at the
bottom of the column on which they appear. Precede the footnote block
with a horizontal rule.\footnote{Sample of the second footnote.}

\subsection{Tables}

Number tables consecutively. Place the table number and title (in
10~point) above the table with one line space above the caption and
one line space below it, as in Table~\ref{sample-table}. You may float
tables to the top or bottom of a column, or set wide tables across
both columns.

\begin{table}[!ht]
\begin{center} 
\caption{Sample table title.} 
\label{sample-table} 
\vskip 0.12in
\begin{tabular}{ll} 
\hline
Error type    &  Example \\
\hline
Take smaller        &   63 - 44 = 21 \\
Always borrow~~~~   &   96 - 42 = 34 \\
0 - N = N           &   70 - 47 = 37 \\
0 - N = 0           &   70 - 47 = 30 \\
\hline
\end{tabular} 
\end{center} 
\end{table}

\subsection{Figures}

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10~point, after the figure with one line space
above the caption and one line space below it, as in
Figure~\ref{sample-figure}. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

\begin{figure}[ht]
\begin{center}
\fbox{CoGNiTiVe ScIeNcE}
\end{center}
\caption{This is a figure.} 
\label{sample-figure}
\end{figure}

>>>>

\title{TODO title}

\author{{\large \bf Jan Gosmann (jgosmann@uwaterloo.ca)} \\
  %Department of Psychology, 1202 W. Johnson Street \\
  %Madison, WI 53706 USA
  \AND{\large \bf Aaron Voelker (TODO)} \\
  \AND{\large \bf Chris Eliasmith (TODO)}
  %Department of Educational Psychology, 1025 W. Johnson Street \\
  %Madison, WI 53706 USA}
  }

@@

\section{Introduction}
Winner-take-all (WTA) mechanisms are often employed in cognitive models. For 
example, TODO O'Reilly, Nengo cleanup, TCM\@. A WTA mechanism receives 
a $d$-dimensional input of utility values for $d$ different choices. The output 
is supposed to be larger than zero for the dimension with highest utility and 
zero for all other inputs.

A large body of literature exists examining how well different WTA mechanisms 
can fit different data from decision experiments (TODO references). Here, 
however, we will investigate the suitability of two different WTA mechanisms in 
the context of large-scale cognitive modelling with spiking neurons on a set of 
benchmarks that are more normative in nature.  The first mechanism is an 
implementation of the classic Usher-McClelland (TODO ref) leaky, competing 
accumulator model.  It has been widely used, for example in versions of the TCM 
model (TODO ref), and TODO some of our models. We will compare this to an 
independent accumulator model with a second thresholding layer with recurrent 
connections to the first layer. In both cases we are especially interested in 
situations with more than two ($d > 2$) choices.

For the implementation of these models we use the Neural Engineering Framework 
(NEF) which allows us to directly implement the prescribed dynamics with spiking 
neurons. The NEF has been used in a wide range of models TODO, including the 
largest functional brain model Spaun (TODO ref). We will give a short 
introduction to the NEF first, then describe the implementation of the two WTA 
mechanisms. In section TODO, we give the results on a number of metrics, 
followed by a discussion in section TODO\@.

\section{Methods}

\subsection{The Neural Engineering Framework}

\subsection{Leaky, competing accumulator model}

\subsection{Independent accumulator model}

* ever increasing evidence
